---
title: "Real Estate Price Prediction Using Elasticnet Regression Analysis"
author: "Bedrock Analytics"
date: "February 17, 2019"
output: 
  pdf_document:
    fig_caption: yes
  pandoc_args: [
      "--number-sections",
      "--number-offset=1"
    ]

params:
  dat_data: NA
  
---
<style type="text/css">

h1.title {
  font-size: 24px;
  font-weight: normal;
}
h3 {
  font-weight:normal;
}
.reveal section img { 
  background:none; 
  border:none; 
  box-shadow:none; 
  }
</style>

```{r include=FALSE}
knitr::opts_chunk$set(comment = NA)
```


```{r,echo=FALSE,warning=FALSE,message=FALSE, error=FALSE}
library(caret)
library(knitr)
library(elasticnet)
library(glmnet) # Package to fit ridge/lasso/elastic net models
library(DMwR)
library(boot) # Package to do bootstrap error estimates
library(prettyR)
library(xtable)
#dat <- params$dat_data
#knitr::kable(dat)
``` 


```{r, echo=FALSE}
# Load data file
dat <- read.csv(file='ason1.csv')
# read chunk (does not run code)

read_chunk('BEDROCK-ELASTICNET-LARS_TRIMMED.R')
read_chunk('BEDROCK-HELP-FUNC.R')

dataIn <- dat
indx <- sapply(dataIn, is.factor)
dataIn[indx] <- lapply(dataIn[indx], function(x) as.numeric(x))
```
Input data file 

# Summary Statistics
```{r  descriptive_stat, results='asis', echo = FALSE}
# Sumary of unscaled predictor (x) variables  
```


```{r standardize_xy, echo=FALSE}
# standardiize xy variables
```

# Correlations Between Predictors
```{r corr_plot, echo=FALSE}
# Plot the correlations between predictors
```

# Tuning Parmenter Selection Using Leave-One-Out Cross Validation
```{r loocv, echo=FALSE, fig.width=7,fig.height=6,fig.cap="\\label{fig:figs}plotting example"}
# results from Loocv
```
`r sprintf("From above plot, lambda =%.2f and s =%.2f gives the minimum RMSE model."
                        ,best.lambda, best.fraction) `


# Variable Importance
```{r var_importance,results='asis',echo=F,warning=F}
#print(plot(varImp(train.enet)))
```

# Standardized Model Coefficients
```{r  best_model, echo = F}
```
```{r  predict_coef, echo = F, results='asis', echo = FALSE}
```

NOTE errors are not given for the predicted coefficients since it is yet unclear how meaningful the std. errors are in penalized regression.


# Model Prediction
```{r predict_price, echo = F, results ='asis'}
```


