---
title: "Real Estate Price Prediction Using Elasticnet Regression Analysis"
author: "Bedrock Analytics"
date: "February 17, 2019"
output: 
  pdf_document:
  #number_sections: true
  pandoc_args: [
      "--number-sections",
      "--number-offset=1"
    ]

params:
  dat_data: NA
  
---
<style type="text/css">

h1.title {
  font-size: 24px;
  font-weight: normal;
}
h3 {
  font-weight:normal;
}
.reveal section img { 
  background:none; 
  border:none; 
  box-shadow:none; 
  }
</style>

```{r include=FALSE}
knitr::opts_chunk$set(comment = NA)
```


```{r,echo=FALSE,warning=FALSE,message=FALSE, error=FALSE}
library(caret)
library(knitr)
library(elasticnet)
library(glmnet) # Package to fit ridge/lasso/elastic net models
library(DMwR)
library(boot) # Package to do bootstrap error estimates
library(prettyR)
library(xtable)
#dat <- params$dat_data
#knitr::kable(dat)
``` 


```{r,echo=F}
dat <- read.csv(file='ason1.csv')

# read chunk (does not run code)
```{r echo=FALSE}
read_chunk('BEDROCK-ELASTICNET-LARS_TRIMMED.R')
read_chunk('BEDROCK-HELP-FUNC.R')

dataIn <- dat
indx <- sapply(dataIn, is.factor)
dataIn[indx] <- lapply(dataIn[indx], function(x) as.numeric(x))
```

# Summary Statistics
```{r  descriptive_sat, echo = FALSE}
```
```{r, results='asis', echo = FALSE}
bold <- function(x) {paste('{\\textbf{',x,'}}', sep ='')}
print(xtable(data.t, 
             digits=0,  
             align= "|l|c|r|r|r|r|",
             caption = "Summary statistics. Note that Mean and Std. Dev. are meaningless for categorical variables."), 
      comment=FALSE, 
      sanitize.colnames.function=bold,
      sanitize.rownames.function=bold, 
      booktabs=F,
      floating = TRUE, latex.environments = "center")

```

```{r standardize_xy, echo=FALSE}
```

# Correlations Between Predictors
```{r corr_plot, echo=FALSE}
```







